|

### 2024-04-22 paper/paper.Rmd
update diagram

@@

```{r pcp, fig.cap = "Parallel coordinate plots of decisions made by computer vision model, conventional tests and visual tests made by human.", eval = TRUE}
library(ggpcp)
mutate(experiment, type = ifelse(type == "polynomial", "Non-linearity", "Heteroskedasticity")) %>%
  mutate(type = factor(type, levels = c("Non-linearity", "Heteroskedasticity"))) %>%
  filter(!null_lineup, !attention_check) %>%
  select(type, actual_ss, model_reject_20, reject, conventional_reject) %>%
  mutate(test = rnorm(n())) %>%
  mutate(across(c(model_reject_20, conventional_reject, reject), ~ifelse(.x, "Reject", "Not reject"))) %>%
  mutate(agree = model_reject_20 == reject) %>%
  pcp_select(c(reject, model_reject_20, conventional_reject)) %>%
  group_by(type) %>%
  pcp_scale() %>%
  ungroup() %>%
  pcp_arrange(method = "from-right") %>%
  ggplot() +
  geom_pcp(aes_pcp(), linewidth = 0.1) +
  geom_pcp_labels(aes_pcp()) +
  geom_pcp_boxes(aes_pcp(), boxwidth = 0.1) +
  facet_wrap(~type) +
  theme_light() +
  scale_x_discrete(labels = c("Visual test", "Computer vision model", "Conventional test")) +
  labs(col = "D") +
  ylab("") +
  xlab("") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
        axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        axis.title = element_blank())
```

@@

>>>>

```{r out.width = "100%", fig.cap = "Diagram of the architecture of the optimized computer vision model."}
knitr::include_graphics("cnn.pdf")
```

@@

```{r pcp, fig.cap = "Parallel coordinate plots of decisions made by computer vision model, conventional tests and visual tests made by human.", eval = TRUE}
library(ggpcp)
mutate(experiment, type = ifelse(type == "polynomial", "Non-linearity", "Heteroskedasticity")) %>%
  mutate(type = factor(type, levels = c("Non-linearity", "Heteroskedasticity"))) %>%
  filter(!null_lineup, !attention_check) %>%
  select(type, actual_ss, model_reject_20, reject, conventional_reject) %>%
  mutate(test = rnorm(n())) %>%
  mutate(across(c(model_reject_20, conventional_reject, reject), ~ifelse(.x, "Reject", "Not reject"))) %>%
  mutate(agree = model_reject_20 == reject) %>%
  pcp_select(c(reject, model_reject_20, conventional_reject)) %>%
  group_by(type) %>%
  pcp_scale() %>%
  ungroup() %>%
  pcp_arrange(method = "from-right") %>%
  ggplot() +
  geom_pcp(aes_pcp(), linewidth = 0.1) +
  geom_pcp_labels(aes_pcp()) +
  geom_pcp_boxes(aes_pcp(), boxwidth = 0.1) +
  facet_wrap(~type, scales = "free_y") +
  theme_light() +
  scale_x_discrete(labels = c("Visual test", "Computer vision model", "Conventional test")) +
  labs(col = "D") +
  ylab("") +
  xlab("") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
        axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        axis.title = element_blank())
```

@@

# Extension to other types of regression model

- Use raw residuals.
  - D for null plots will be greater than zero.
  - Can not assume D for actual plots are greater than D for null plots any more.
  - Need to use a two-sided test instead of a one-sided test.
  - It may fail completely due to the identification issue.
- Use transformed residuals that roughly follow a multivariate normal distribution.
  - The one-sided test will still work. 
  - Need to ensure that the transformed actual plot will have residual distribution different from the transformed null distribution. 
- Train a new model.
  - KL divergence may not be the appropriate measure for the difference between the residual distributions. Could consider using a new distance measure.
  -
